---
title: "Showing Relationships between CSDs using Network Analysis in R"
output: html_notebook
---

# Introduction

Showing relationships between different market Code Subsidiary Documents (CSDs) and how they reference each other. 


```{r}

library(pdftools)
library(tidyverse)
library(stringr)
library(igraph)
library(networkD3)
library(htmlwidgets)
library(arcdiagram)

```


Converting PDFs to text files using pdftools. 

```{r}

csd_docs <- list.files("documents", pattern = "CSD")

csd_text <- list()

for (csd in csd_docs) {
  csd_url <- paste0(getwd(), "/documents/", csd)
  temp <- paste(pdf_text(csd_url), collapse = " ")
  csd_text <- append(csd_text, temp)
}

csd_list <- str_sub(csd_docs, 1, 8)

```


Counting references to CSDs in each document. 


```{r}

csd_count_df <- NULL

for (i in 1:length(csd_list)) {
  
  temp_df <- data.frame(
    CsdRef = csd_list[i],
    CsdEntity = csd_list,
    CsdCount = str_count(csd_text[i], csd_list)
  )
  
  csd_count_df <- rbind(csd_count_df, temp_df)
  
}
    
csd_network <- csd_count_df %>% 
  mutate(SelfReference = CsdRef == CsdEntity) %>% 
  filter(CsdCount > 0, !SelfReference) %>% 
  select(-SelfReference)

head(csd_network)

```


From this we see that of the `r NROW(csd_list)` documents

Showing the counts


```{r}

plot1 <- csd_network %>% 
  group_by(CsdEntity) %>% 
  summarise(CsdCount = sum(CsdCount)) %>% 
  ggplot() + 
  geom_col(aes(reorder(CsdEntity, -CsdCount), CsdCount)) + 
  coord_flip()

plot2 <- csd_network %>% 
  ggplot() + 
  geom_bar(aes(fct_infreq(CsdEntity))) + 
  coord_flip()

combined_plots <- gridExtra::arrangeGrob(plot1, plot2, ncol = 2)

plot(combined_plots)

```


Exploring different ways of visualising the relationships using network graphs and different layouts


```{r}

csd_network_graph <- csd_network %>% 
  graph_from_data_frame(directed = FALSE) 

csd_network_graph %>% 
  plot(
    layout = layout.random, 
    main = "random"
  )

csd_network_graph %>% 
  plot(
    layout = layout.circle, 
    main = "circle"
  )

csd_network_graph %>% 
  plot(
    vertex.size = degree(graph_from_data_frame(csd_network), mode = "all"), 
    layout = layout.fruchterman.reingold, 
    main = "fruchterman.reingold"
    )


```

Individual sta diagrams

```{r}

csd_network_graph %>% 
  #filter(CsdRef == "CSD 0301") %>% 
  graph.star()


```




Arch diagram

```{r}

csd_edges <- get.edgelist(csd_network_graph)

arcplot(csd_edges, sorted = TRUE, decreasing = TRUE, las = 2)

```



```{r}

csd_degree <- degree(csd_network_graph)

arcplot(csd_edges, cex.nodes = csd_degree / 10, show.nodes = TRUE)


```

